---
title: Smart Save CSV
output: github_document
author: 
- family: Varadharajan
  given: Dwaraknaath
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Objective of this package

This package allows users to combine two dataframes with similar column headers and classes. Also, there is an option to remove duplicates using value column. valuecol parameter is passed on to the function. The function removes duplicate rows by looking at all the column header except the ones mentioned in the valuecol parameter. There are many use cases for this package, especially related to saving time specific information. For example, lets say the user has weather information for the last 365 days and also 7 days in the future. Weather information for the days in the past does not change but the weather forecast for the next 7 days keep changing as we move further into the future. This package plays an important role when we have to combined the existing weather information, with all the latest information that is going to come in the future. Sufficient examples are illustrated below to save the user from any confusion. 

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
